---
output:
  md_document:
    variant: gfm
html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

# rfastqQC: The quality evaluation

```{r, echo=FALSE, results="hide", message=FALSE}
Biocpkg <- function (pkg) {
    sprintf("[%s](http://bioconductor.org/packages/%s)", pkg, pkg)
}
```

```{r comment="", echo=FALSE, results='asis'}
cat(packageDescription('rfastqQC')$Description)
```

## :writing_hand: Authors

[Shuangbin Xu](https://github.com/xiangpin)

School of Basic Medical Sciences, Southern Medical University

## :arrow_double_down: Installation

The development version from github:

```r
if (!requireNamespace("remotes", quietly=TRUE))
    install.packages("remotes")
remotes::install_github("xiangpin/rfastqQC")
```

## :sparkling_heart: Contributing

We welcome any contributions! Please note that the 'rfastqQC' project is released with a [Contributor Code of Conduct](CONDUCT.md). By contributing to this project, you agree to abide by its terms.
